Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-27 manuscript/manuscript.tex
started to outline materials and methods

>>>>

\subsection*{Influenza hemagglutinin sequences.}
We downloaded all full-length protein-coding sequences for each of the 18 influenza HA subtypes. 
We used \texttt{phydms\_prepalignment} \citep{hilton2017phydms} to filter and align the sequences. 
We subsampled to five per year plus the required sequences.
